Missing the Point: Non-Convergence in Iterative Imputation Algorithms

### 2020-05-01 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Add critical value to plot for AC

```{r diagnostics, fig.cap="Convergence diagnostics applied on the imputation algorithms of Figure 2."}
load("./images/diagnostics_plot.Rdata") #bquote(theta ~ "= chain mean in "~ y[imp][",m"])
diagnostics_plot
```

@@

@@

```{r mean, fig.height = 6.8, fig.cap="Convergence diagnostics chain mean."}
mean_Rh + mean_AC + mean_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= chain mean of Y in" ~ y[imp][",m"] ~ "; Q = " ~ mu[Y] ~ "= 25.81"))
```

```{r sd, fig.height = 6.8, fig.cap="Convergence diagnostics chain variance."}
var_Rh + var_AC + sd_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= chain variance of Y in" ~ y[imp][",m"] ~ "; Q = " ~ sigma[Y] ~ "= 11.32"))
```
```{r est, fig.height = 6.8, fig.cap="Convergence diagnostics regression coefficient."}
est_Rh + est_AC + est_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= " ~ hat(beta)[2] ~ "in {" ~ y[obs] ~ "," ~ y[imp][",m"] ~ "}" ~ "; Q = " ~ beta[2] ~ "= 2.06"))
```

```{r pred, fig.height = 6.8, fig.cap="Convergence diagnostics regression coefficient."}
PCA_Rh + PCA_AC + Rsq_bias + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = "Performance of convergence diagnostics", subtitle = bquote(theta ~ "= first eigenvalue of" ~ Sigma ~ "in {" ~ y[obs] ~ "," ~ y[imp][",m"] ~ "}" ~ "; Q = explained variance = 19.25"))

>>>>

```{r diagnostics, fig.cap="Convergence diagnostics applied on the imputation algorithms of Figure 2. $\\theta$ = chain mean in $y_{imp, m}$."}
load("./images/diagnostics_plot.Rdata") #bquote(theta ~ "= chain mean in "~ y[imp][",m"])
diagnostics_plot 
```

@@

We want to know what the effect is of inducing non-conv of the bias in all Qs and the confidence validity of the betas. So we plot the bias for each Q against the number of iterations in the condition and the missingness proportion in the condition. We look at averages across simulation repetitions. Then, we want to know if conditions in which the Qs are affected by non-convergence (on average) are also identified by the conv diag. We do this by looking at the bias in Q against the

@@

```{r mean, fig.height = 6.8, fig.cap="Convergence diagnostics chain mean."}
mean_bias + mean_Rh + mean_AC + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = bquote("Q = " ~ mu[Y] ~ "= 25.81; " ~ theta ~ "= chain mean of Y in" ~ y[imp][",m"])) #& theme(legend.position = "bottom")
```

```{r sd, fig.height = 6.8, fig.cap="Convergence diagnostics chain variance."}
sd_bias + var_Rh + var_AC + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = bquote("Q = " ~ sigma[Y] ~ "= 11.32; " ~ theta ~ "= chain variance of Y in" ~ y[imp][",m"]))
```

```{r est, fig.height = 6.8, fig.cap="Convergence diagnostics regression coefficient."}
est_bias + est_Rh + est_AC + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = bquote("Q = " ~ beta[2] ~ "= 2.06; " ~ theta ~ "= " ~ hat(beta)[2] ~ "in {" ~ y[obs] ~ "," ~ y[imp][",m"] ~ "}"))
```

```{r pred, fig.height = 6.8, fig.cap="Convergence diagnostics regression coefficient."}
Rsq_bias + PCA_Rh + PCA_AC + plot_layout(guides = "collect", ncol = 1) + plot_annotation(tag_levels = "A", tag_suffix = ".", title = bquote("Q = " ~ r^2 ~ "\u00D7 100 = 19.25; " ~ theta ~ "= " ~ lambda[1] ~ "in {" ~ y[obs] ~ "," ~ y[imp][",m"] ~ "}")) #first eigenvalue of" ~ Sigma ~ 
```
